### 2017-09-22 Sections/economics_of_the_quantum_internet.tex
Touch up indexing

\begin{figure}[htb!]\index{Network price scaling factor}
	\includegraphics[width=\columnwidth]{network_price_scaling_factor}
	\caption{Scaling of the network price scaling factor, $\chi_\text{sc}$, as a function of several representative computational scaling functions, $f_\text{sc}$, where $n$ is network size.} \label{fig:NPSF}
\end{figure}

@@

Now, if \mbox{$Q=1$} we have the breakeven point, whereby investment into physical hardware is profit-neutral in payback. If \mbox{$Q<1$} we spend more on hardware than we gain from its use and run at a loss. But if \mbox{$Q>1$} we can make guaranteed profit by investing in new hardware. The perfect price competition assumption (Pos.~\ref{post:market_eff}) will drive the market price towards the zero-profit breakeven point (but not quite -- someone has to make money!), such that \mbox{$Q\gtrapprox 1$}. That is, the economic gain approximates the hardware investment,
\begin{align} \label{sec:gain_eq_invest}
	n_\text{gain}(t) \gtrapprox n_\text{invest}(t).
\end{align}

@@

Additionally, we have assumed no compute-cycles are wasted -- compute-time is always fully utilised, as per Pos.~\ref{post:market_eff}. Then it follows that the time-share of the combined resources of the entire network should be unity,
\begin{align}
	r_{n_\text{global}}=1.
\end{align}
\mbox{$r_{n_\text{global}}<1$} would imply inefficiency via wasted clock-cycles. Combining this with the linearity constraint implies the arbitrage-free time-sharing model,
\begin{definition}[Arbitrage-free time-sharing model] \label{def:arb_free_ts}\index{Arbitrage-free time-sharing model}
In an efficient market for unified quantum computing time-shares, a network participant in possession of $n$ of the entire $n_\text{global}$ qubits in the network is entitled to the fraction of unified network compute time,
\begin{align}\index{Time-shared compute-time}
	r_n = \frac{n}{n_\text{global}},
\end{align}
where,
\begin{align}
n_\text{global} = \sum_{j\in\text{nodes}} n_j,
\end{align}
is the total number of qubits in the network, and,
\begin{align}
0\leq r_n \leq 1.	
\end{align}
\mbox{$r_n=1$} iff the node has a complete monopoly over qubits, i.e \mbox{$n=n_\text{global}$}.

@@

Suppose Alice and Bob both possessed expensive classical Cray\texttrademark\, supercomputers, both identical. They're both connected to the internet, so does it make sense to unify their computational resources over the network to construct a more powerful virtual machine\index{Virtual quantum computer}, which they subsequently time-share\index{Time-sharing} between themselves, or are they better off just using their own computers independently?

>>>>

\begin{figure}[htb!]\index{Network price scaling factor}
	\includegraphics[width=\columnwidth]{network_price_scaling_factor}
	\caption{Scaling of the network price scaling factor, $\chi_\text{sc}$, as a function of several representative computational scaling functions, $f_\text{sc}$, where $n$ is network size.\comment{Colours are fucked.}} \label{fig:NPSF}
\end{figure}

@@

Now, if \mbox{$Q=1$} we have the breakeven point, whereby investment into physical hardware is profit-neutral in payback. If \mbox{$Q<1$} we spend more on hardware than we gain from its use and run at a loss. But if \mbox{$Q>1$} we can make guaranteed profit by investing in new hardware. The perfect price competition assumption (Pos.~\ref{post:market_eff}) will drive the market price towards the zero-profit breakeven point (but not quite -- someone has to make money!), such that \mbox{$Q\gtrapprox 1$}. That is, the economic gain approximates the hardware investment, with $Q\to 1$ driven ever closer to unity as market competition increases, thereby closing the gap between investment and reward,
\begin{align} \label{sec:gain_eq_invest}
	n_\text{gain}(t) \gtrapprox n_\text{invest}(t).
\end{align}

@@

Additionally, we have assumed no compute-cycles are wasted -- compute-time is always fully utilised, as per Pos.~\ref{post:market_eff}. Then it follows that the time-share of the combined resources of the entire network should be unity,
\begin{align}
	r_{n_\text{global}}=1.
\end{align}
\mbox{$r_{n_\text{global}}<1$} would imply inefficiency via wasted clock-cycles. Combining this with the linearity constraint implies the arbitrage-free time-sharing model,
\begin{definition}[Arbitrage-free time-sharing model] \label{def:arb_free_ts}\index{Arbitrage-free time-sharing model}
In an efficient market for unified quantum computing time-shares\index{Time-shares}\comment{Check index for doubling up}, a network participant in possession of $n$ of the entire $n_\text{global}$ qubits in the network is entitled to the fraction of unified network compute time,
\begin{align}\index{Time-shared compute-time}
	r_n = \frac{n}{n_\text{global}},
\end{align}
where,
\begin{align}
n_\text{global} = \sum_{j\in\text{nodes}} n_j,
\end{align}
is the total number of qubits in the network, and,
\begin{align}
0\leq r_n \leq 1.	
\end{align}
\mbox{$r_n=1$} iff the node has a complete monopoly over qubits, i.e \mbox{$n=n_\text{global}$}.

@@

Suppose Alice and Bob both possessed expensive classical Cray\texttrademark\, supercomputers\index{Supercomputers}, both identical. They're both connected to the internet, so does it make sense to unify their computational resources over the network to construct a more powerful virtual machine\index{Virtual quantum computer}, which they subsequently time-share\index{Time-sharing} between themselves, or are they better off just using their own computers independently?
